Viscous Transport in Eroding Porous Media

### 2019-05-10 docs/transport/erosion_transport.tex
working on early sections of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing on our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
double-layer potential can be as the sum of the Laplace double-layer
potential and its gradient.  By identifying $\xx,\yy \in \RR^2$ with the
points $x,y \in \CC$, the Laplace double-layer potential for a
real-valued density function $\eta$ can also be written as the real part
of the Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy = 
  \Re \left( \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy \right).
\end{align}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and its first derivative.  In addition, we also require
expressions for the derivative of the velocity field which can be
written in terms of a Cauchy integral and its first two derivatives.
Therefore, we introduce the notation
\begin{align}
  \label{eqn:cauchy}
  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,  \quad
  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^3} \, dy.
\end{align}
To simplify notation, whenever it will not cause confusion, we exclude
$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
\end{align}
All these integrals but the first are a gradient of a Laplace layer
potential with the density functions $\eta_1$, $\eta_2$, and $\yy \cdot
\eeta$.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued
densities~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)),\\
  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of $\nn \in \RR^2$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
To compute the rate of erosion, we must compute the shear stress of the
double-layer potential
\begin{align}
  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
\end{align}
where $\nn$ and $\ss$ are the unit normal and tangent vectors at $\xx$,
respectively.  Each term of the gradient of the velocity field can be
written in terms of Cauchy integrals as
\todo[inline]{not clear enough how we got these equations.  Need to show
how we do one of them and say the rest are calculated similarly.}
\begin{align}
  \pderiv{u_1}{x_1}(\xx) &= \Re (v'[\tau_1](x)) + 
    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
  \pderiv{u_1}{x_2}(\xx) &= - \Im (v'[\tau_1](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_1}(\xx) &= \Re (v'[\tau_2](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_2}(\xx) &= -\Im (v'[\tau_2](x)) - 
    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
\end{align}
\todo[inline]{S-H: last term seems to be missing an $x_1$.  Some of the
other terms seem to be a bit off.  It might be partially my fault from
when I updated some of the tex.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Vorticity}
Having calculated all derivatives of the double-layer potential, the
vorticity can written in terms of Cauchy integrals.  In particular
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\end{align}
\todo[inline]{For S-H to fill in}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Boundary Integral Equation Formulation}
\label{s:formulation}
Continuing with our previous work~\cite{qua-moo2018}, we use a completed
double-layer potential formulation for the velocity $\uu$.  The
double-layer potential is
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
  \label{eqn:stokesDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, $\nn$ is the unit outward
normal at $\yy$, and $\eeta$ is an unknown density function.  The Stokes
double-layer potential can be as the sum of the Laplace double-layer
potential and its gradient.  By identifying $\xx,\yy \in \RR^2$ with the
points $x,y \in \CC$, the Laplace double-layer potential for a
real-valued density function $\eta$ can also be written as the real part
of the Cauchy integral
\begin{align}
  \DD[\eta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega}
    \frac{\rr \cdot \nn}{\rho^2} \eta(\yy) ds_\yy = 
  \Re \left( \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy \right).
\end{align}
Therefore, the Stokes double-layer potential can be written in terms of
Cauchy integrals and its first derivative.  In addition, we also require
expressions for the derivative of the velocity field which can be
written in terms of a Cauchy integral and its first two derivatives.
Therefore, we introduce the notation
\begin{align}
  \label{eqn:cauchy}
  v[\eta](x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x - y} \, dy,  \quad
  v'[\eta](x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^2} \, dy, \quad
  v''[\eta](x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{(x - y)^3} \, dy.
\end{align}
To simplify notation, whenever it will not cause confusion, we exclude
$\tau$ and instead write $v(x)$, $v'(x)$, and $v''(x)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Double-Layer
Potential}
The Stokes double-layer potential~\eqref{eqn:stokesDLP} can be
decomposed as
\begin{align}
  \DDD[\eeta](\xx) &= 
    \frac{1}{2\pi} \int_{\Gamma} 
      \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
    \frac{1}{2\pi} \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
    &- \frac{1}{2\pi} x_1 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
    \frac{1}{2\pi} x_2 \nabla \int_{\Gamma}
      \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
\end{align}
All these integrals but the first are a gradient of a Laplace layer
potential.  In addition, each component of the first integral can be
written as a Cauchy integral with a complex-valued density
function~\cite{bar-wu-vee2015}.  Therefore, the Stokes double-layer
potential can be written as five Cauchy integrals and their derivatives
with the density functions $\yy \cdot \eeta$, $\eta_1$, and $\eta_2$.
The individual velocity components are
\begin{align}
  \label{eqn:cauchy1}
  u_1(\xx) &= \Re (v[\tau_1](x)) + \Re (v'[\yy\cdot\eeta](x)) 
           -x_1\Re (v'[\eta_1](x)) - x_2\Re (v'[\eta_2](x)), \\
  u_2(\xx) &= \Re (v[\tau_2](x)) - \Im (v'[\yy\cdot\eeta](x)) 
       +x_1\Im (v'[\eta_1](x)) + x_2\Im (v'[\eta_2](x)),
\end{align}
where
\begin{align} 
  \tau_1=(\eta_1+i\eta_2)\frac{\Re(n)}{n}, \quad \text{and} \quad
  \tau_2=(\eta_1+i\eta_2)\frac{\Im(n)}{n},
\end{align}
and $n \in \CC$ is the complex representation of the outward unit normal
$\nn \in \RR^2$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Shear Stress}
To compute the rate of erosion, we must compute the shear stress of the
double-layer potential
\begin{align}
  \tau(\xx) = \left(\nabla \DDD[\eeta](\xx) + 
    \nabla^T \DDD[\eeta](\xx) \right) \nn \cdot \ss,
\end{align} where $\nn$ and $\ss$ are the unit normal and tangent
vectors at $\xx$, respectively.  Each term of the gradient of the
velocity field can be written in terms of Cauchy integrals.  For
example,
\begin{align}
  \pderiv{u_1}{x_2} &= \Re(iv'[\tau_1](x)) + 
      \Re(i v''[\yy \cdot \nn](x)) -
      x_1\Re(i v''[\eta_1](x))  -
      \Re(v'[\eta_2](x)) - x_2 \Re(iv''[\eta_2](x)) \\
    &= -\Im(v''[\tau_1](x)) - 
      \Im(v''[\yy \cdot \nn](x)) +
      x_1\Im(v''[\eta_1](x)) -
      \Re(v'[\eta_2](x)) + x_2 \Im(v''[\eta_2](x)).
\end{align}
Similarly, the other three components of $\nabla \DDD[\eeta]$ can be
calculated
\begin{align}
  \pderiv{u_1}{x_1} &= \Re (v'[\tau_1](x)) + 
    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x)), \\
  \pderiv{u_1}{x_2} &= - \Im (v'[\tau_1](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_1} &= \Re (v'[\tau_2](x)) - 
    \Im (v''[\yy\cdot\eeta](x)) + \Im (v'[\eta_1](x)) +
    x_1\Im (v''[\eta_1](x)) + x_2\Im (v''[\eta_2](x)), \\
  \pderiv{u_2}{x_2} &= -\Im (v'[\tau_2](x)) - 
    \Re (v''[\yy\cdot\eeta](x)) + x_1\Re (v''[\eta_1](x)) +
    \Im (v'[\eta_2](x)) + x_2\Re (v''[\eta_2](x)).
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cauchy Integral Representation of the Vorticity}
Having calculated all derivatives of the double-layer potential, the
vorticity can written in terms of Cauchy integrals.  In particular,
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
\Re (v'[\tau_2](x)) + \Im (v'[\tau_1](x)) 
 + \Re (v'[\eta_2](x))+ \Im (v'[\eta_1](x)).
\end{align}

@@

%{\color{red}
%Here we derive the equations~\eqref{eqn:pderiv1}-\eqref{eqn:pderiv2} 
%and the other two are similar.
%To derive equations~\eqref{eqn:pderiv1} and \eqref{eqn:pderiv2}, 
%we need to apply the fact that if a real function $u$ is equivalent to 
%the real part of a complex varaible function $f$, 
%then we have $\nabla u=(\Re(f'),-\Im(f'))$.
%Let $f_1(x)= v[\tau_1](x)$, $f_2(x)=v'[\yy\cdot\eeta](x)$, $f_3(x)=v'[\eta_1](x)$,
%and $f_4(x)= v'[\eta_2](x)$. Then we can rewrite equation~\eqref{eqn:cauchy1}
%\begin{align*}
%u_1(\xx)&= u_{11}(\xx) +  u_{12}(\xx) +u_{13}(\xx)+u_{14}(\xx) \\
%&=\Re (f_1(x)) + \Re (f_2(x))-x_1\Re (f_3(x)) - x_2\Re (f_4(x)).
%To get the gradient of $u_1(x)$, we have
%\begin{align*}
%\nabla u_1(x)&= \nabla u_{11}(x)+\nabla  u_{12}(x) 
%+\nabla u_{13}(x)+\nabla u_{14}(x) \\ \\
%&=\begin{bmatrix}
%\Re(f_1'(x))\\ \\
%-\Im(f_1'(x))
%\end{bmatrix}+
%\begin{bmatrix}
%\Re(f_2'(x))\\ \\
%-\Im(f_2'(x))
%\end{bmatrix}
%+
%\begin{bmatrix}
%-\Re(f_3(x))-x_1\Re(f_3'(x))\\ \\
%x_1\Im(f_3'(x))
%\end{bmatrix}
%+
%\begin{bmatrix}
%-x_2\Re(f_4'(x))\\ \\
%-\Re(f_4(x))+x_2\Im(f_4'(x))
%\end{bmatrix}\\ \\
%&=
%\begin{bmatrix}
%\Re (v'[\tau_1](x)) + 
%    \Re (v''[\yy\cdot\eeta](x)) - \Re (v'[\eta_1](x)) - 
%    x_1\Re (v''[\eta_1](x)) - x_2\Re (v''[\eta_2](x))\\ \\
%- \Im (v'[\tau_1](x)) - 
%    \Im (v''[\yy\cdot\eeta](x)) + x_1\Im (v''[\eta_1](x)) - 
%    \Re (v'[\eta_2](x)) + x_2\Im (v''[\eta_2](x))
%\end{bmatrix}.
